\documentclass[a4paper, 12pt]{article}
\author{Justin L. Clough, 
        Irina K. Tezaur,
        Assad A. Oberai}
\title{Convergence Study for Tetrahedrons with Composite, Quadratic, and Linear Shape Functions in Bending}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{subfigure}
\usepackage[justification=centering]{caption}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{listings}
\lstset{
    escapechar=`,
    language=C++,
    numbers=left,
    tabsize=2,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=single,
    breaklines=true,
}
\usepackage{graphicx}
\graphicspath{ {./} }
\usepackage{nameref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{tikz}
\usetikzlibrary{calc,patterns,decorations.pathmorphing,decorations.markings,positioning,automata}
\usepackage{pgfplots}
\pgfplotsset{compat=1.5}
\usepackage{pgfplotstable}
\usepackage{makecell}
\usepackage{verbatim}
\usepackage[super]{nth}

\begin{document}
\maketitle

\begin{abstract}
The convergence of tetrahedral elements with
\nth{2} order shape functions are compared to those with composite
and linear shape functions
in a beam bending problem.
A linear elastic material model was used
and no time components were considered.
The geometry was a beam with a square cross-section and 
aspect ratio of 100.
The beam was cantilevered on one end and received a 
shearing traction at the other. 
The tip deflection of the finite element solutions were
compared to that from Euler-Bernoulli beam theory. 
Tetrahedrons with \nth{2} order and composite shape functions under-predicted
the theoretical solution by less than 1\% with 2 elements 
through the thickness of the beam;
elements with linear shape functions under-predicted 
the theoretical solution by 99\% with 16 elements through the thickness.
\end{abstract}

\section{Introduction}
The performance of tetrahedron elements with \nth{2} order shape functions
was compared to that of elements with composite
(discussed in \cite{bib:composite_tet})
and linear shape functions in a beam-bending problem.
The mesh was refined such that the aspect ratio of the elements
stayed at 10 as the number of elements through the thickness was increased.
The theoretical deflection from Euler-Bernoulli beam theory was used to
compared the finite element results.

\section{Methods}
The problem geometry was a beam with a square cross-section.
The cross-section was 0.01 m $ \times $ 0.01 m; 
the beam was 1 m long in the $Y$ direction.
The other edges of the beam were aligned with the $X$ and $Z$ axes.

A linear elastic material model was used. 
Young's Modulus was 4000 Pa;
Poisson's ratio was 0.25.
No time components were considered
and only the static solution was calculated.

The square face with normal in the negative $Y$ direction had 
all degrees of freedom fixed to act as a cantilever support. 
The face on the other end of the beam received a 
traction of 0.01 $\frac{N}{m^2}$ in the $Z$ direction.
From Euler-Bernoulli beam theory, the tip deflection
is modeled as:

\begin{equation}
  \delta = \frac{F L^3}{3 E I}
  \label{eq:EB_deflection}
\end{equation}

\noindent
where 
$F$ is the total force acting at the tip of the beam, 
$L$ is the length of the beam,
$E$ is Young's Modulus for the beam's material,
and
$I$ is the second moment of the cross-sectional area.
Evaluating Equation (\ref{eq:EB_deflection}) for the
given parameters of the problem, 
the theoretical tip deflection is 0.1 m.

A mesh was constructed to approximate the beam geometry
and used only tetrahedral elements.
The convergence of 
tetrahedrons with \nth{2} order (quadratic tet10 elements),
composite, and linear shape functions
were separately measured.
An aspect ratio of 10 was used for all meshes
and the number of elements through the thickness of the beam was increased.
A direct linear algebra solver was used to solve the system.

\section{Results}
The tip deflections from the finite element solutions
are shown with respect to the number of degrees of freedom 
in Figure \ref{fig:convergence}.
Four meshes were constructed with 1, 2, 4, and 8 elements
through the thickness.

\begin{figure}[H]
  \centering
    \begin{tikzpicture}
      \begin{axis}[
        legend pos=outer north east,
        legend cell align={left},
        grid=both,
        grid style={line width=.1pt, draw=gray!10},
        major grid style={line width=.2pt,draw=gray!50},
        xtick={},
        ytick={},
        ymax=0.11,
        minor tick num=5,
        title=Convergence of Tip Deflection,
        xlabel=Degrees of Freedom,
        yticklabel style={/pgf/number format/.cd,fixed,fixed zerofill,precision=4,/tikz/.cd},
        ylabel={Tip Deflection [m]} ]
        \addplot table {quadratic_data_beam.txt};
          \addlegendentry{Quadratic}
        \addplot table {composite_data_beam.txt};
          \addlegendentry{Composite}
        \addplot table {linear_data_beam.txt};
          \addlegendentry{Linear}
      \end{axis}
    \end{tikzpicture}
  \caption{Tip deflection for beam geometry with composite and quadratic elements.
           The number of elements through the thickness was 1, 2, 4, and 8.
           Analytical solution is 0.1 m.}
  \label{fig:convergence}
\end{figure}

The quadratic and composite tet10 elements underestimated the tip deflection 
within 2\% of the analytical solution with 4 elements through
the thickness. 
The linear elements underestimated 
the analytical solution by more than 99\% in all cases.


\newpage
\begin{thebibliography}{99}

\bibitem{bib:composite_tet}
J. T. Ostien,
J. W. Foulk,
A. Mota,
M. G. Veilleux.
A 10-node Composite tetrahedral finite element for solid mechanics.
International Journal For Numerical Methods in Engineering.
2016:107:1145-1170. 

\end{thebibliography}


\end{document}
